---
title: "RNAmodR.Data: example data for RNAmodR packages"
author: "Felix G.M. Ernst and Denis L.J. Lafontaine"
date: "`r Sys.Date()`"
package: RNAmodR
output:
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{RNAmodR.Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown(css.files = c('custom.css'))
```

# Available resources

`RNAmodR.Data` contains example data for the `RNAmodR` and related 
packages. The data is provided as gff3, fasta and bam files.

Four sets of data with multiple files are included

```{r, echo=FALSE}
suppressPackageStartupMessages({
  library(RNAmodR.Data)
})
```
```{r, eval=FALSE}
library(RNAmodR.Data)
```

```{r}
eh <- ExperimentHub()
ExperimentHub::listResources(eh, "RNAmodR.Data")
```

These resources are grouped based on topic. Please have a look at the following
man pages:

- `?RNAmodR.Data.example` for general example data used for different purposes
- `?RNAmodR.Data.RMS` for example data for RiboMethSeq
- `?RNAmodR.Data.AAS` for example data for AlkAnilineSeq
- `?RNAmodR.Data.man` for small data set for man page examples
- `?RNAmodR.Data.snoRNAdb` for snoRNAdb as csv file

# Sessioninfo

```{r}
sessionInfo()
```
